refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-08-10 paper/manuscript.tex
PAPER: include autocorrelation plot in notebook;

\begin{figure}
  \includegraphics[width=175mm]{./supporting_information/corner.pdf}
  \caption{Corner plot for the varying parameters of DMPC bilayers supported on a silicon crystal, measured at three contrasts. The sampling took $\sim$\SI{13}{\minute} on a \SI{3.2}{GHz} quad-core computer for 30 saved steps, corresponding to 6000 samples, with the steps being thinned by a factor of 100. A larger scale image is available in supporting information.}
  \label{fig:corner}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=175mm]{./supporting_information/corner.pdf}
  \caption{Corner plot for the varying parameters of DMPC bilayers supported on a silicon crystal, measured at three contrasts. The sampling took $\sim$\SI{41}{\minute} on a \SI{2.8}{GHz} quad-core computer for 16 saved steps, corresponding to 4800 samples, with the steps being thinned by a factor of 500. A larger scale image is available in supporting information.}
  \label{fig:corner}
\end{figure}
